Update Meeting: 15-10-2021

### 2022-04-20 analysis/update_meeting_15_10_2021.Rmd
add some final manuscript files

Decided best to also include all $X$ IVs in the model as well. MRMR model is: $Y_p \sim Y_i + X_i$.

@@

## merge the list of dataframes 
corr_impact_by_PCs.DT <- replace_Neale_ID(corr_impact_by_PCs, traits_corr2_filled, "Neale_pheno_ID", "outcome_description")
format_round_cols <- colnames(dplyr::select_if(corr_impact_by_PCs.DT, is.numeric))
DT::datatable(corr_impact_by_PCs.DT, width = "100%")  %>% formatRound(columns=format_round_cols, digits = 3)

@@

```{r coordin_traits_confounding, echo = FALSE, eval = ifelse(Sys.info()["sysname"]=="Linux", TRUE, FALSE)}

## merge the list of dataframes 
corr_impact_by_coords.DT <- replace_Neale_ID(corr_impact_by_coords, traits_corr2_filled, "Neale_pheno_ID", "outcome_description")
format_round_cols <- colnames(dplyr::select_if(corr_impact_by_coords.DT, is.numeric))
DT::datatable(corr_impact_by_coords.DT, width = "100%")  %>% formatRound(columns=format_round_cols, digits = 3)

>>>>

Decided best to also include all $X$ IVs in the model as well. MVMR model is: $Y_p \sim Y_i + X_i$.

@@

corr_impact_by_PCs.DT <- replace_Neale_ID(corr_impact_by_PCs, traits_corr2_filled, "Neale_pheno_ID", "outcome_description")
format_round_cols <- colnames(dplyr::select_if(corr_impact_by_PCs.DT, is.numeric))
DT::datatable(corr_impact_by_PCs.DT, width = "100%")  %>% formatRound(columns=format_round_cols, digits = 3)

@@

```{r coord_traits_confounding, echo = FALSE, eval = ifelse(Sys.info()["sysname"]=="Linux", TRUE, FALSE)}

corr_impact_by_coords.DT <- replace_Neale_ID(corr_impact_by_coords, traits_corr2_filled, "Neale_pheno_ID", "outcome_description")
format_round_cols <- colnames(dplyr::select_if(corr_impact_by_coords.DT, is.numeric))
DT::datatable(corr_impact_by_coords.DT, width = "100%")  %>% formatRound(columns=format_round_cols, digits = 3)
